---
title: "COVID 19 Report"
author:
- familyname: Zhang
  othernames: Lintian
  address: Monash Universtiy
  email: ltzha1@student.monash.edu
  correspondingauthor: true
  qualifications:  Bachelor of Accounting
- familyname: Widjaya
  othernames: Arthur Andersen
  address: Monash University
  email: awid0001@student,monash.edu
  correnpondingauthor: true
  qualifications: Bachelor of Accounting
- familyname: Wang
  othernames: Hanchen
  address: Monash University
  email: hwan0143@student.monash.edu
  correspondingauthor: true
  qualifications:  Bachelor of Finance
- familyname: Zou
  othernames: Ying
  address: Monash University
  email: yzou0014@student.monash.edu
  correspondingauthor: true
  qualifications: Bachelor of Economics
department: Team Amazing
organization: Australian Government COVID19
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
  always_allow_html: true
header-includes:
 \usepackage{float}
 \floatplacement{figure}{H}
 \floatplacement{table}{H}
---

```{r , echo = FALSE, message = FALSE, warning = FALSE}
# Libraries

library(tidyverse)
library(readr)
library(kableExtra)
library(stargazer)
library(PerformanceAnalytics)
library(tidyverse)
library(bookdown)

```


# Introduction



\section*{Total cases in Australia}

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
covid <- read_csv("Data/All.csv")
```

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
covid_long <- covid %>% 
  mutate(date = as.Date(date, '%d-%b')) %>% 
  pivot_longer(cols = -date,
             names_to = "state",
             values_to = "Count") 
  dates <- unique(sort(covid_long$date)) 
  covid_long$date <- factor(covid_long$date, ordered = T)
```

# Total COVID 19 cases from each state in the last 28 days

```{r table1, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
table <- covid_long %>% 
  group_by(state) %>% 
  summarise(total = sum(Count)) %>% 
  arrange(desc(total))

knitr::kable(table, caption = "Total cases in 28 days") %>% 
kable_classic(full_width = F, html_font = "Cambria")
```

## Analysis 

table \@ref(tab:table1) shows the total number of COVID 19 cases from all the states in Australia in the last 28 days. It clearly shows that in the last 28 days New South Wales (NSW) has added the most number of cases with total of 211 cases. Compared to other states they only at 50's cases with Australian Capital Territory (ACT) and Tasmania (TAS) only added 1 and 0 cases. It reflects that NSW has been struggling. The data was downloaded as in 18 of May 2021, they really need to increase their attention in order to contain the virus outbreak. 

# Highest and lowest COVID 19 cases in Australia 

```{r, fig.width=10, figref1, fig.cap = "Highest and lowest COVID 19 cases in Australia", eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(covid_long,
       aes(x = reorder(date, -Count),
y = Count, fill = state)) +
  geom_col() +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust = 1)) +
expand_limits(x = c(0, NA), y = c(0, NA)) + 
scale_y_continuous(labels = scales::label_number_si())  +xlab("date") + ggtitle("Highest and lowest COVID 19 cases in Australia")

```

## Analysis 

Figure \@ref(fig:figref1) showing the highest  to lowest cases of COVID 19 the X axis acts recorded the date on when the case was recorded. At glance at the 23 of April 2021 the day where Australia adds the higest total cases with NSW is the highest contributor, and the lowest cases was recorded at 14 May 2021.

# COVID 19 cases in Australia in the last 28 days

```{r figref2, fig.cap = "Daily cases in Australia in the last 28 days", eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
 ggplot(covid_long,
       aes(x = date,
y = Count, fill = state)) +
  geom_col() +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust = 1)) +
expand_limits(x = c(0, NA), y = c(0, NA)) + 
scale_y_continuous(labels = scales::label_number_si()) + ggtitle("Daily cases in Australia in the last 28 days")
```

## Analysis 

\@ref(fig:figref2) showing the COVID 19 cases trends from 16 of April to 18 of May 2021. During the first few weeks the cases has rises and reaches it's peak on the 22 April 2021. 2 days later it drops and suddenly there has been an increase again. But overall during the last 28 days Australia has shown a great way to contain the outbreak on the first week which showing the efficiency of the government rules and regulation. 

\section*{Recovery}



\section*{Transmission sources of daily cases in Australia}
```{r message=FALSE, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
transmission <- read_csv("Data/National.csv")
```

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
transmission <- transmission %>% 
  mutate(date = as.Date(date, '%d-%b'))
```

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
transmission_long <- transmission %>% 
  mutate(date = as.Date(date, '%d-%b')) %>% 
  pivot_longer(cols = -date,
             names_to = "source",
             values_to = "Count")
dates <- unique(sort(transmission_long$date)) 
transmission_long$date <- factor(transmission_long$date, ordered = T)
 
```

```{r tra, fig.cap = "Transmission sources of daily cases 20 April 2021 - 18 May 2021", fig.align = 'center', eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
  
c <- ggplot(transmission_long, aes(x = date,
y = Count, fill = source)) +
  geom_col() +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust = 1)) +
expand_limits(x = c(0, NA), y = c(0, NA)) + 
scale_y_continuous(labels = scales::label_number_si())+
  labs(x= "Date", 
       y = "Number of cases")

c
```


The figure \@ref(fig:tra) indicates that the most of transmissions were from overseas. Especially, there were more than 35 cases from overseas recorded and one case was due to the interstate travel in 23 April. Only One case is under investigation which has been recorded in 5 May.

Luckily, there are no more local community spread in Australia from 20 April 2021 to 18 May 2021.




\section*{Vaccination in Australia}


## Vaccination Rates
```{r}
library(hrbrthemes)
vaccine <- read_csv(here::here("Data/Total doses.csv"))
```

```{r} 
 vaccine_long <- vaccine %>% 
  mutate(date=as.Date(date,'%d-%b'))
dates <- unique(sort(vaccine_long$date))
vaccine_long$date <- factor(vaccine_long$date,ordered=T)
```

```{r FigRefplot, fig.cap = "Vaccination Rates Over Time", warning = FALSE }
  ggplot(vaccine_long,
         aes(x=date,y=`Per 100 people (right axis)`))+
  geom_point(size=2,alpha=0.3,color='#b3699f')+
  ylab("vaccination Rates(per 100 people)")+
  xlab("Date")+
  theme(plot.title = element_text(h = 0.5))+
  scale_color_manual(values = colors)+
    theme_ipsum() + theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust = 1))
```



The graph \@ref(fig:Figplot) shows a general upward trend in vaccination, with the vaccination rate starting to show a faster increase in early April. The vaccination rate grows faster and faster over time. The number of vaccinations reached 12.39% on May 18. The increase in vaccination rates illustrates the importance the government places on the outbreak.



## Vaccination Coverage

```{r FigRefz, fig.align = "center",fig.cap = "Increase in vaccination coverage over time",message=FALSE, warning=FALSE}
ggplot(vaccine_long, 
       aes(x = date,
           y = `Total doses (left axis)`)) +
  geom_col()+
    xlab("Date") +
    ylab("Vaccine") +
    theme_ipsum() + theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust = 1))+ theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust = 1)) 
```


We can see from the graph \@ref(fig:FigRefz) that the number of inoculations continues to grow, from 20 people on February 21 to 3,183,324 people on May 18. The rate of growth has been accelerating since the beginning of April.

# Conclusion


