---
title: "COVID 19 Report"
author:
- familyname: Zhang
  othernames: Lintian
  address: Monash Universtiy
  email: ltzha1@student.monash.edu
  correspondingauthor: true
  qualifications:  Bachelor of Accounting
- familyname: Widjaya
  othernames: Arthur Andersen
  address: Monash University
  email: awid0001@student,monash.edu
  correnpondingauthor: true
  qualifications: Bachelor of Accounting
- familyname: Wang
  othernames: Hanchen
  address: Monash University
  email: hwan0143@student.monash.edu
  correspondingauthor: true
  qualifications:  Bachelor of Finance
- familyname: Zou
  othernames: Ying
  address: Monash University
  email: yzou0014@student.monash.edu
  correspondingauthor: true
  qualifications: Bachelor of Economics
department: Team Amazing
organization: Australian Government COVID19
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
  always_allow_html: true
header-includes:
 \usepackage{float}
 \floatplacement{figure}{H}
 \floatplacement{table}{H}
---

```{r , echo = FALSE, message = FALSE, warning = FALSE}
# Libraries

library(tidyverse)
library(readr)
library(kableExtra)
library(stargazer)
library(PerformanceAnalytics)
library(tidyverse)
library(bookdown)

```


# Introduction



\section*{Total cases in Australia}


\section*{Recovery}



\section*{Transmission sources of daily cases in Australia}
```{r message=FALSE}
transmission <- read_csv("Data/National.csv")
```

```{r}
transmission <- transmission %>% 
  mutate(date = as.Date(date, '%d-%b'))
```

```{r}
transmission_long <- transmission %>% 
  mutate(date = as.Date(date, '%d-%b')) %>% 
  pivot_longer(cols = -date,
             names_to = "source",
             values_to = "Count")
dates <- unique(sort(transmission_long$date)) 
transmission_long$date <- factor(transmission_long$date, ordered = T)
 
```

```{r tra, fig.cap = "Transmission sources of daily cases 20 April 2021 - 18 May 2021", fig.align = 'center', fig.width=10, echo=FALSE, warning=FALSE, message=FALSE}
  
c <- ggplot(transmission_long, aes(x = date,
y = Count, fill = source)) +
  geom_col() +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust = 1)) +
expand_limits(x = c(0, NA), y = c(0, NA)) + 
scale_y_continuous(labels = scales::label_number_si())+
  labs(x= "Date", 
       y = "Number of cases")

c
```


The figure \@ref(fig:tra) indicates that the most of transmissions were from overseas. Especially, there were more than 35 cases from overseas recorded and one case was due to the interstate travel in 23 April. Only One case is under investigation which has been recorded in 5 May.

Luckily, there are no more local community spread in Australia from 20 April 2021 to 18 May 2021.




\section*{Vaccination in Australia}



# Conclusion


